### 2024-01-28 ms.qmd
bayes_R2

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards. Final sample sizes per treatment and species are disclosed on @tbl-data.  
```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
## A.1) L. delicata
deli_red <- fit_m("deli", "red", refit = FALSE)
write.csv(deli_red, file= "./output/Checking/deli_red.csv")
deli_blue <- fit_m("deli", "blue", refit = FALSE)
write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
## A.2) L. guichenoti
guich_red <- fit_m("guich", "red", refit = FALSE)
write.csv(guich_red, file= "./output/Checking/guich_red.csv")
guich_blue <- fit_m("guich", "blue", refit = FALSE)
write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
```

>>>>

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards. Final sample sizes per treatment and species are disclosed on @tbl-data.  
```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
## A.1) L. delicata
deli_red <- fit_m("deli", "red", refit = FALSE)
bayes_R2(deli_red)

write.csv(deli_red, file= "./output/Checking/deli_red.csv")
deli_blue <- fit_m("deli", "blue", refit = FALSE)
write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
## A.2) L. guichenoti
guich_red <- fit_m("guich", "red", refit = FALSE)
write.csv(guich_red, file= "./output/Checking/guich_red.csv")
guich_blue <- fit_m("guich", "blue", refit = FALSE)
write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
```
